\documentclass[11pt]{article}

\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=black]{hyperref}

\usepackage[english]{babel}

\title{\underline{Project defense}}

\begin{document}
\title{\underline{Project defence - AutoPylot}}
\date{}
\maketitle
Members : Alexandre Girold, Mickael Bobovitch, Maxime Ellerbach, Maxime Gay.
\section{Introduction}
An overall look at our project.\\ 
Project : An autonomous vehicle. \\
Objective : Make an autonomous car which can race on a given track without human input for direction or speed.

\section{Common and individual tasks}

\begin{tabular}{|c|c|c|c|}
\hline
  Alexandre &
  Maxime.G &
  Maxime.E &
  Mickael \\ \hline
  \begin{tabular}[c]{@{}c@{}}Introduction\\ Quick Recap\\ Website Presentation\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Data Gathering\\ Training\\ Conclusion\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Label Zones\\ Simulator\\ Race \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Installation\\ Telemetry Server \\ Race\end{tabular} \\ \hline
\end{tabular}

\section {Description of the realization of the tasks}

\begin{itemize}
 
\item Quick Recap: Recap of previous project defenses. 
\item Label Zones: Creation of label zones to improve car speed. 
\item Installation: Installation of the project.
\item Presentation Website: Showcase our project.
\item Data Gathering: How do we gather data. 
\item Training: Training of our model.
\item Simulator: Gathering data with an online simulator.
\item Telemetry server: Send telemetry to an external server.
\item The Race: Demonstration on track.
\item Conclusion: What are we planning for the future.

\end{itemize}

\section {Conclusion}

\begin{itemize}
\item Recap of what we have said.
\item Done : We improved our training model and the telemetry server. We also created a simulator to train our model. 

\item To do : We have to win the Vivatech race.

\end{itemize}


\end{document}
