\documentclass[11pt]{article}

\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=black]{hyperref}

\usepackage[english]{babel}

\title{\underline{Project defense}}

\begin{document}
\maketitle
Members : Alexandre Girold, Mickael Bobovitch, Maxime Ellerbach, Maxime Gay.
\section{Introduction}
An overall look at our project.\\ 
Project : An autonomous vehicle. \\
Objective : Make an autonomous car which can race on a given track without human input for direction or speed.

\section{Common and individual tasks}

\begin{tabular}{|c|c|c|c|c|}
\hline
Common &
  Alexandre &
  Maxime.G &
  Maxime.E &
  Mickael \\ \hline
\begin{tabular}[c]{@{}c@{}}T-shirt\\ Organisation\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Load and Save Data\\ Data set\\ Logo\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Load and Save Data\\ Data Set\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Arduino \\ Car control\\ Data Vis\\ Camera\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Website\\ Basic car loop\end{tabular} \\ \hline
\end{tabular}

\section {Description of the realization of the tasks}

\begin{itemize}

\item Arduino and car control: Drive the car using code. % Ellerbach
\item Data handling and visualization: Load, save and visualize data. % Girold and Gay
\item Logging and Telemetry server: Log events and send telemetry to an external server. % Ellerbach and Bobovitch
\item Basic car loop: Put everything together to drive the car with a controller. % Bobovitch
\item Creation of the logo: Our visual identity % Girold
\item Presentation Website: Showcase our project. % Bobovitch

\end{itemize}

\section {Conclusion}

\begin{itemize}
\item Recap of what we have said.
\item Done : Control of the car with a controller and data processing are working flawlessly.

\item To do : Working on the AI part of the car to have it working by the next as well as a website for telemetry.
\end{itemize}


\end{document}
