\documentclass[11pt]{article}

\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=black]{hyperref}

\usepackage[english]{babel}

\title{\underline{Project defense}}

\begin{document}
\title{\underline{Project defence - AutoPylot}}
\date{}
\maketitle
Members : Alexandre Girold, Mickael Bobovitch, Maxime Ellerbach, Maxime Gay.
\section{Introduction}
An overall look at our project.\\ 
Project : An autonomous vehicle. \\
Objective : Make an autonomous car which can race on a given track without human input for direction or speed.

\section{Common and individual tasks}

\begin{tabular}{|c|c|c|c|c|}
\hline
Common &
  Alexandre &
  Maxime.G &
  Maxime.E &
  Mickael \\ \hline
\begin{tabular}[c]{@{}c@{}}T-shirt\\ Modularity\\ Organisation\\ Neural network \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Load \& Save Data\\ Data set\\ Datagenerator\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Load \& Save Data\\ Data set\\Datagenerator \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Arduino\\ Car Control \& Camera\\ Data Vis\\ Model training\\ Simulator \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Website\\ Basic Car Loop\\ Telemetry server\\ Simulator\end{tabular} \\ \hline
\end{tabular}

\section {Description of the realization of the tasks}

\begin{itemize}

\item Presentation Website: Showcase our project. % Bobovitch
\item Arduino and car control: Drive the car using code. % Ellerbach
\item Data handling and visualization: Load, save and visualize data. % Girold and Gay
\item Logging and Telemetry server: Log events and send telemetry to an external server. % Ellerbach and Bobovitch
\item Basic car loop: Put everything together to drive the car with a controller. % Bobovitch
\item Modularity of the project. % Girold
\item Datagenerator: Data handling. % Girold and Gay
\item Neural network: Training a model. % Ellerbach
\item Data augmentation: To avoid overfit % Gay
\item Simulator: gathering data with an online simulator % Ellerbach

\end{itemize}

\section {Conclusion}

\begin{itemize}
\item Recap of what we have said.
\item Done : We improved our training model and the telemetry server. We also created a simulator to train our model. 

\item To do : We have to win the Vivatech race.

\end{itemize}


\end{document}
