\documentclass[11pt]{article}

\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=black]{hyperref}

\usepackage[english]{babel}

\title{\underline{Project defense}}

\begin{document}
\maketitle
Members : Alexandre Girold, Mickael Bobovitch, Maxime Ellerbach, Maxime Gay.
\section{Introduction}
An overall look at our project.\\ 
Project : An autonomous vehicle. \\
Objective : Make an autonomous car which can race on a given track without human input for direction or speed.

\section{Common and individual tasks}

\begin{tabular}{|c|c|c|c|c|}
\hline
Common &
  Alexandre &
  Maxime.G &
  Maxime.E &
  Mickael \\ \hline
\begin{tabular}[c]{@{}c@{}}T-shirt\\ Modularity \\ Organisation\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Datagenerator \\ Neural network \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Datagenerator \\ Neural network \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Model training \\ Neural network \end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Website\\ Telemetry server \\ Neural network\end{tabular} \\ \hline
\end{tabular}

\section {Description of the realization of the tasks}

\begin{itemize}

\item Modularity of the project % Girold
\item Data handling: Datagenerator. % Girold and Gay
\item Training a model: neural network. % Ellerbach
\item Data augmentation. % Gay
\item Telemetry server. % Bobovitch 
\item Presentation website: Showcase our project. % Bobovitch

\end{itemize}

\section {Conclusion}

\begin{itemize}
\item Recap of what we have said.
\item Done : We made a telemetry server to have real time data of the car as the video and notifications. We also have a working model.

\item To do : Improve the AI part. We would like to have a dynamic management of the speed. For the telemetry server we would like to add some charts corresponding to the throttle and the steering. \\
And of course we have to win some races.

\end{itemize}


\end{document}
